\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}

\usepackage[pdftex]{graphicx}
%\usepackage[caption=false,font=footnotesize]{subfig}
%\usepackage{url}
%\usepackage{multirow}
%\usepackage{subfigure}
%\usepackage{caption}
\usepackage[caption=false]{subfig}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{color}
\usepackage{balance}
%\usepackage{hyperref}
%\setlength{\textfloatsep}{5pt}

\usepackage{algorithmic}
\usepackage{pseudocode}
\usepackage[linesnumbered,vlined,ruled]{algorithm2e}
\usepackage{threeparttable}
\usepackage{comment}
\usepackage{todonotes}
\usepackage{tabu}
\usepackage[justification=centering]{caption}
\usepackage{soul}
\usepackage{adjustbox}
\usepackage{commath}
\usepackage[acronym]{glossaries}
\usepackage{titlesec}
\usepackage[hidelinks=true]{hyperref}


%\usepackage{mathptmx}
%\DeclareCaptionFont{xipt}{\fontsize{11}{13}\mdseries}
%\usepackage[font=xipt,labelfont=bf]{caption}
%\usepackage[font=times]{caption}
%\usepackage[font=rm]{caption}

% \newfontfamily{\ubuntufont}{Times NeW Roman}
% \DeclareCaptionFont{ubuntu}{\ubuntufont}
\usepackage[font={footnotesize}]{caption}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}


\title{IEEE~802.11ah Restricted Access Window Surrogate Model for Real-Time Station Grouping}



% \title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
% \tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.
% }

%% Group authors per affiliation:
% \author{\IEEEauthorblockN{Le~Tian\IEEEauthorrefmark{1}, Michael~Mehari\IEEEauthorrefmark{2}, Serena~Santi\IEEEauthorrefmark{1}, Steven~Latr\'e\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\ Eli~De~Poorter\IEEEauthorrefmark{2}, Jeroen Famaey\IEEEauthorrefmark{1}}
% \IEEEauthorblockA{\IEEEauthorrefmark{1}University of Antwerp - imec, IDLab, Department of Mathematics and Computer Science, Belgium}
% \IEEEauthorblockA{\IEEEauthorrefmark{2}Ghent University - imec, IDLab, Department of Information Technology, Belgium}}
\author[1]{Le Tian}
\ead{le.tian@uantwerpen.be}

\author[2]{Michael~Mehari}
\ead{michael.mehari@ugent.be}

\author[1]{Serena~Santi}
\ead{Serena.Santi@uantwerpen.be}

\author[1,2]{Steven~Latr\'e}
\ead{Steven.Latre@uantwerpen.be}

\author[2]{Eli~De~Poorte}
\ead{eli.depoorter@ugent.be}

\author[1]{Jeroen Famaey }
\ead{jeroen.famaey@uantwerpen.be}


\address[1]{University of Antwerp - imec, IDLab, Department of Mathematics and Computer Science, Belgium}
\address[2]{Ghent University - imec, IDLab, Department of Information Technology, Belgium}
%\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
% \author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
% \ead[url]{www.elsevier.com}

% \author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
% \cortext[mycorrespondingauthor]{Corresponding author}
% \ead{support@elsevier.com}

%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

\input{glossary}

%\maketitle

\begin{abstract}
The \gls{raw} mechanism proposed by IEEE~802.11ah promises to address one of the major problems of the \gls{iot}: high channel contention in large-scale densely deployed sensor networks. The \gls{raw} feature allows the \gls{ap} to divide stations into different groups, with only the stations in the same group being allowed to access the channel simultaneously. Existing station grouping strategies only support homogeneous scenarios, where all sensor stations have the same fixed data transmission interval, \gls{mcs} and packet size. In this paper, we present two contributions to address this issue. %First, a surrogate model that predicts \gls{raw} performance given specific network conditions and \gls{raw} configuration parameters. It is fast to train and can be solved in real-time. 
%Second, the \gls{moroa}, which uses the surrogate model to determine the optimal \gls{raw} configuration in real-time, for heterogeneous stations and dynamic traffic. 
\textcolor{red}{First, surrogate models that predict \gls{raw} performance (e.g., throughput, energy) given specific network conditions and \gls{raw} configuration parameters. The models are fast to train and can be solved in real-time. 
Second, the \gls{moroa}, which uses the surrogate models to determine the \gls{raw} configuration in real-time to optimize multiple objectives, for heterogeneous stations and dynamic traffic.} We compare the accuracy of our surrogate model to %\textcolor{red}{ a state of the art analytical model}, as well as 
simulation results. Performance of \gls{moroa} is compared to existing \gls{raw} optimization algorithms and traditional 802.11 channel access methods.
%The results shows that the trained surrogate model can accurately predict \gls{raw} performance with a relative error less than 7\% and 10\% for 95\% and 98\% of the \gls{raw} configurations respectively. \gls{moroa} achieves a throughput up to twice as high as traditional 802.11 channel access functions in dense heterogeneous networks.
\textcolor{red}{
The results shows that the trained surrogate models can accurately predict \gls{raw} performance with a relative error less than 7\% and 10\% for 90\% and 95\% of the \gls{raw} configurations, respectively. \gls{moroa} achieves  65\% higher throughput and 96\% less energy consumption than traditional 802.11 channel access functions in dense heterogeneous networks.}
\end{abstract}

\begin{keyword}
IEEE 802.11ah, restricted access window (RAW), surrogate model, real-time station grouping, multi-objective optimization
\end{keyword}

% IEEE 802.11ah; dense IoT networks; restricted access window (RAW); real-time RAW
% 22 optimization; dynamic traffic

\end{frontmatter}

\linenumbers

\glsresetall


\input{input/introduction}
\input{input/related_work}
%\input{input/80211ah}
\input{input/SUMO}
\input{input/algorithm}
\input{input/evaluation}
\input{input/conclusion}


\section*{Acknowledgement}
Part of this research was funded by the Flemish FWO SBO S004017N IDEAL-IoT (Intelligent DEnse And Long range IoT networks) project. Serena Santi is funded by the Fund For Scientific Research (FWO) Flanders under grant number 1S82118N.


\bibliographystyle{IEEEtran}
\bibliography{references.bib}








\end{document}